### 2024-04-15 docs/projects/datavis/ggplot/draft.qmd
ggplot - rerendered

::: {.printedClojure}
```clojure
{:layers
 [{:aes_params {:size [5.0]},
   :stat {:compute_layer :ggproto-method, :super :ggproto-method},
   :show.legend [nil],
   :mapping {:colour [~ cyl]},
   :super :ggproto-method,
   :inherit.aes [true],
   :geom_params {:na.rm [false]},
   :geom
   {:non_missing_aes ["size" "shape" "colour"],
    :draw_key :ggproto-method,
    :default_aes
    {:shape [19.0],
     :colour ["black"],
     :size [1.5],
     :fill [nil],
     :alpha [nil],
     :stroke [0.5]},
    :super :ggproto-method,
    :required_aes ["x" "y"],
    :draw_panel :ggproto-method},
   :stat_params {:na.rm [false]},
   :constructor {: nil, :mapping {: nil, :color cyl}, :size [5.0]},
   :position {:compute_layer :ggproto-method, :super :ggproto-method},
   :data []}],
 :scales
 {:scales
  [{:labels [],
    :scale_name ["position_c"],
    :breaks [],
    :call
    {:labels labels,
     :scale_name ["position_c"],
     :breaks breaks,
     :name name,
     :palette identity,
     :super ScaleContinuousPosition,
     :guide guide,
     :minor_breaks minor_breaks,
     :n.breaks n.breaks,
     : nil,
     :aesthetics [$ ggplot_global y_aes],
     :na.value na.value,
     :trans trans,
     :oob oob,
     :position position,
     :limits limits,
     :expand expand},
    :rescaler :ggproto-method,
    :name [],
    :palette :ggproto-method,
    :super :ggproto-method,
    :guide [],
    :minor_breaks [],
    :n.breaks nil,
    :aesthetics
    ["y"
     "ymin"
     "ymax"
     "yend"
     "yintercept"
     "ymin_final"
     "ymax_final"
     "lower"
     "middle"
     "upper"
     "y0"],
    :na.value [nil],
    :trans
    {:name ["identity"],
     :transform
     "function (x) \nx\n<bytecode: 0x5b75ae3c23a0>\n<environment: namespace:base>\n",
     :inverse
     "function (x) \nx\n<bytecode: 0x5b75ae3c23a0>\n<environment: namespace:base>\n",
     :breaks
     "function (x, n = n_default) \n{\n    x <- x[is.finite(x)]\n    if (length(x) == 0) {\n        return(numeric())\n    }\n    rng <- range(x)\n    labeling::extended(rng[1], rng[2], n, ...)\n}\n<bytecode: 0x5b75b232cda8>\n<environment: 0x5b75bd6e2898>\n",
     :minor_breaks
     "function (b, limits, n) \n{\n    b <- b[!is.na(b)]\n    if (length(b) < 2) {\n        return()\n    }\n    bd <- diff(b)[1]\n    if (!reverse) {\n        if (min(limits) < min(b)) \n            b <- c(b[1] - bd, b)\n        if (max(limits) > max(b)) \n            b <- c(b, b[length(b)] + bd)\n    }\n    else {\n        if (max(limits) > max(b)) \n            b <- c(b[1] - bd, b)\n        if (min(limits) < min(b)) \n            b <- c(b, b[length(b)] + bd)\n    }\n    seq_between <- function(a, b) {\n        seq(a, b, length.out = n + 1)[-(n + 1)]\n    }\n    breaks <- unlist(Map(seq_between, b[-length(b)], b[-1]))\n    breaks <- c(breaks, b[length(b)])\n    breaks\n}\n<bytecode: 0x5b75b23326a8>\n<environment: 0x5b75bd6e2710>\n",
     :format
     "function (x) \n{\n    if (!is.null(names(x))) {\n        return(names(x))\n    }\n    ret <- format(x, ..., trim = TRUE, justify = \"left\")\n    ret[is.na(x)] <- NA\n    ret\n}\n<bytecode: 0x5b75b2335cd0>\n<environment: 0x5b75bd6e2198>\n",
     :domain [##-Inf ##Inf]},
    :oob :ggproto-method,
    :position ["left"],
    :limits [20.0 30.0],
    :expand [],
    :range {:super :ggproto-method}}],
  :super :ggproto-method},
 :mapping {:x [~ cty], :y [~ hwy]},
 :theme [],
 :coordinates
 {:expand [true],
  :clip ["on"],
  :limits {:x nil, :y nil},
  :super :ggproto-method,
  :default [true]},
 :facet {:shrink [true], :super :ggproto-method},
 :labels {:x ["cty"], :y ["hwy"], :colour ["cyl"]}}

@@

     "function (x) \nlog(x, base)\n<bytecode: 0x5b75b7b00b30>\n<environment: 0x5b75b582d0a0>\n",

@@

     "function (x) \nbase^x\n<bytecode: 0x5b75b7b00f90>\n<environment: 0x5b75b582d0a0>\n",

@@

     "function (x, n = n_default) \n{\n    raw_rng <- suppressWarnings(range(x, na.rm = TRUE))\n    if (any(!is.finite(raw_rng))) {\n        return(numeric())\n    }\n    rng <- log(raw_rng, base = base)\n    min <- floor(rng[1])\n    max <- ceiling(rng[2])\n    if (max == min) {\n        return(base^min)\n    }\n    by <- floor((max - min)/n) + 1\n    breaks <- base^seq(min, max, by = by)\n    relevant_breaks <- base^rng[1] <= breaks & breaks <= base^rng[2]\n    if (sum(relevant_breaks) >= (n - 2)) {\n        return(breaks)\n    }\n    while (by > 1) {\n        by <- by - 1\n        breaks <- base^seq(min, max, by = by)\n        relevant_breaks <- base^rng[1] <= breaks & breaks <= \n            base^rng[2]\n        if (sum(relevant_breaks) >= (n - 2)) {\n            return(breaks)\n        }\n    }\n    log_sub_breaks(rng, n = n, base = base)\n}\n<bytecode: 0x5b75b7a46af8>\n<environment: 0x5b75b58310d8>\n",

@@

     "function (b, limits, n) \n{\n    b <- b[!is.na(b)]\n    if (length(b) < 2) {\n        return()\n    }\n    bd <- diff(b)[1]\n    if (!reverse) {\n        if (min(limits) < min(b)) \n            b <- c(b[1] - bd, b)\n        if (max(limits) > max(b)) \n            b <- c(b, b[length(b)] + bd)\n    }\n    else {\n        if (max(limits) > max(b)) \n            b <- c(b[1] - bd, b)\n        if (min(limits) < min(b)) \n            b <- c(b, b[length(b)] + bd)\n    }\n    seq_between <- function(a, b) {\n        seq(a, b, length.out = n + 1)[-(n + 1)]\n    }\n    breaks <- unlist(Map(seq_between, b[-length(b)], b[-1]))\n    breaks <- c(breaks, b[length(b)])\n    breaks\n}\n<bytecode: 0x5b75b23326a8>\n<environment: 0x5b75b5830ce8>\n",

@@

     "function (x) \n{\n    if (!is.null(names(x))) {\n        return(names(x))\n    }\n    ret <- format(x, ..., trim = TRUE, justify = \"left\")\n    ret[is.na(x)] <- NA\n    ret\n}\n<bytecode: 0x5b75b2335cd0>\n<environment: 0x5b75b5830b98>\n",

>>>>

::: {.printedClojure}
```clojure
{:layers
 [{:aes_params {:size [5.0]},
   :stat {:compute_layer :ggproto-method, :super :ggproto-method},
   :show.legend [nil],
   :mapping {:colour [~ cyl]},
   :super :ggproto-method,
   :inherit.aes [true],
   :geom_params {:na.rm [false]},
   :geom
   {:non_missing_aes ["size" "shape" "colour"],
    :draw_key :ggproto-method,
    :default_aes
    {:shape [19.0],
     :colour ["black"],
     :size [1.5],
     :fill [nil],
     :alpha [nil],
     :stroke [0.5]},
    :super :ggproto-method,
    :required_aes ["x" "y"],
    :draw_panel :ggproto-method},
   :stat_params {:na.rm [false]},
   :constructor {: nil, :mapping {: nil, :color cyl}, :size [5.0]},
   :position {:compute_layer :ggproto-method, :super :ggproto-method},
   :data []}],
 :scales
 {:scales
  [{:labels [],
    :scale_name ["position_c"],
    :breaks [],
    :call
    {:labels labels,
     :scale_name ["position_c"],
     :breaks breaks,
     :name name,
     :palette identity,
     :super ScaleContinuousPosition,
     :guide guide,
     :minor_breaks minor_breaks,
     :n.breaks n.breaks,
     : nil,
     :aesthetics [$ ggplot_global y_aes],
     :na.value na.value,
     :trans trans,
     :oob oob,
     :position position,
     :limits limits,
     :expand expand},
    :rescaler :ggproto-method,
    :name [],
    :palette :ggproto-method,
    :super :ggproto-method,
    :guide [],
    :minor_breaks [],
    :n.breaks nil,
    :aesthetics
    ["y"
     "ymin"
     "ymax"
     "yend"
     "yintercept"
     "ymin_final"
     "ymax_final"
     "lower"
     "middle"
     "upper"
     "y0"],
    :na.value [nil],
    :trans
    {:name ["identity"],
     :transform
     "function (x) \nx\n<bytecode: 0x5b75ae3c23a0>\n<environment: namespace:base>\n",
     :inverse
     "function (x) \nx\n<bytecode: 0x5b75ae3c23a0>\n<environment: namespace:base>\n",
     :breaks
     "function (x, n = n_default) \n{\n    x <- x[is.finite(x)]\n    if (length(x) == 0) {\n        return(numeric())\n    }\n    rng <- range(x)\n    labeling::extended(rng[1], rng[2], n, ...)\n}\n<bytecode: 0x5b75b232cda8>\n<environment: 0x5b75bd974a08>\n",
     :minor_breaks
     "function (b, limits, n) \n{\n    b <- b[!is.na(b)]\n    if (length(b) < 2) {\n        return()\n    }\n    bd <- diff(b)[1]\n    if (!reverse) {\n        if (min(limits) < min(b)) \n            b <- c(b[1] - bd, b)\n        if (max(limits) > max(b)) \n            b <- c(b, b[length(b)] + bd)\n    }\n    else {\n        if (max(limits) > max(b)) \n            b <- c(b[1] - bd, b)\n        if (min(limits) < min(b)) \n            b <- c(b, b[length(b)] + bd)\n    }\n    seq_between <- function(a, b) {\n        seq(a, b, length.out = n + 1)[-(n + 1)]\n    }\n    breaks <- unlist(Map(seq_between, b[-length(b)], b[-1]))\n    breaks <- c(breaks, b[length(b)])\n    breaks\n}\n<bytecode: 0x5b75b23326a8>\n<environment: 0x5b75bd974b90>\n",
     :format
     "function (x) \n{\n    if (!is.null(names(x))) {\n        return(names(x))\n    }\n    ret <- format(x, ..., trim = TRUE, justify = \"left\")\n    ret[is.na(x)] <- NA\n    ret\n}\n<bytecode: 0x5b75b2335cd0>\n<environment: 0x5b75bd974ce0>\n",
     :domain [##-Inf ##Inf]},
    :oob :ggproto-method,
    :position ["left"],
    :limits [20.0 30.0],
    :expand [],
    :range {:super :ggproto-method}}],
  :super :ggproto-method},
 :mapping {:x [~ cty], :y [~ hwy]},
 :theme [],
 :coordinates
 {:expand [true],
  :clip ["on"],
  :limits {:x nil, :y nil},
  :super :ggproto-method,
  :default [true]},
 :facet {:shrink [true], :super :ggproto-method},
 :labels {:x ["cty"], :y ["hwy"], :colour ["cyl"]}}

@@

     "function (x) \nlog(x, base)\n<bytecode: 0x5b75b7b00b30>\n<environment: 0x5b75bbf72268>\n",

@@

     "function (x) \nbase^x\n<bytecode: 0x5b75b7b00f90>\n<environment: 0x5b75bbf72268>\n",

@@

     "function (x, n = n_default) \n{\n    raw_rng <- suppressWarnings(range(x, na.rm = TRUE))\n    if (any(!is.finite(raw_rng))) {\n        return(numeric())\n    }\n    rng <- log(raw_rng, base = base)\n    min <- floor(rng[1])\n    max <- ceiling(rng[2])\n    if (max == min) {\n        return(base^min)\n    }\n    by <- floor((max - min)/n) + 1\n    breaks <- base^seq(min, max, by = by)\n    relevant_breaks <- base^rng[1] <= breaks & breaks <= base^rng[2]\n    if (sum(relevant_breaks) >= (n - 2)) {\n        return(breaks)\n    }\n    while (by > 1) {\n        by <- by - 1\n        breaks <- base^seq(min, max, by = by)\n        relevant_breaks <- base^rng[1] <= breaks & breaks <= \n            base^rng[2]\n        if (sum(relevant_breaks) >= (n - 2)) {\n            return(breaks)\n        }\n    }\n    log_sub_breaks(rng, n = n, base = base)\n}\n<bytecode: 0x5b75b7a46af8>\n<environment: 0x5b75bbf8dcc8>\n",

@@

     "function (b, limits, n) \n{\n    b <- b[!is.na(b)]\n    if (length(b) < 2) {\n        return()\n    }\n    bd <- diff(b)[1]\n    if (!reverse) {\n        if (min(limits) < min(b)) \n            b <- c(b[1] - bd, b)\n        if (max(limits) > max(b)) \n            b <- c(b, b[length(b)] + bd)\n    }\n    else {\n        if (max(limits) > max(b)) \n            b <- c(b[1] - bd, b)\n        if (min(limits) < min(b)) \n            b <- c(b, b[length(b)] + bd)\n    }\n    seq_between <- function(a, b) {\n        seq(a, b, length.out = n + 1)[-(n + 1)]\n    }\n    breaks <- unlist(Map(seq_between, b[-length(b)], b[-1]))\n    breaks <- c(breaks, b[length(b)])\n    breaks\n}\n<bytecode: 0x5b75b23326a8>\n<environment: 0x5b75bbfa2f60>\n",

@@

     "function (x) \n{\n    if (!is.null(names(x))) {\n        return(names(x))\n    }\n    ret <- format(x, ..., trim = TRUE, justify = \"left\")\n    ret[is.na(x)] <- NA\n    ret\n}\n<bytecode: 0x5b75b2335cd0>\n<environment: 0x5b75bbfa2e10>\n",
